Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Who is scaffolder for in conclusions section

Scaffolder follows the Unix philosophy of ``Do one thing and do it well.''. The
focus of Scaffolder is a simple to use tool for creating a genome scaffold. The
YAML data format for creating the scaffold file is standardised and easily
manipulated programmatically. This thereby means the scaffolding process
follows a second Unix tenet: ``If your data structures are good enough, the
algorithm to manipulate them should be trivial.''.

>>>>

Scaffolder is software aimed at bioinformaticians and biologists familar with
the command line who wish to build scaffold a genome sequence in a concise
readable way. The Scaffolder file format allows other biologists to see how the
genome sequence was assembled and allows a broad overview of how the sequence
was assembled not possible not possible from a megabase-sized string of
nucleotide characters. Scaffolder also furthers the cause for reporducibility
in genome sequence by allowing the scaffold super-sequence to be reliably
reproduced from the scaffold file. \pb

The design of the Scaffolder software follows the Unix philosophy of ``Do one
thing and do it well.''. The focus of Scaffolder is a simple to use tool for
creating a genome scaffold. The YAML data format for creating the scaffold file
is standardised and easily manipulated programmatically. This thereby means the
scaffolding process follows a second Unix tenet: ``If your data structures are
good enough, the algorithm to manipulate them should be trivial.''.
